\documentclass{article}

\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage[left=2cm, right=2cm, top=2cm, bottom=3cm]{geometry}

\textheight=12in
\fontsize{15pt}{30pt}
\pagestyle{empty}
\raggedright



\newcommand{\lineunder}{
	\vspace*{-4pt}\\ 
	\hspace*{-18pt}\hrulefill \\
}

\newcommand{\header}[1]{
	{\hspace*{-15pt}\vspace*{6pt}\textsc{#1}}\vspace*{-6pt}\lineunder
}

\newcommand{\employer}[5]{
	{\textbf{#1}{\hfill\textbf{#2}}\\ 
	{{\emph{#3}}}\hfill {#4}\\ \hfill {#5}}
}

\newcommand{\project}[3]{
	{\textbf{#1} - #2{\hfill\textbf{#3}}\vspace*{3pt}}
}

\newcommand{\contact}[5]{
	\vspace*{-8pt}
	\begin{center}
		{\Large \textbf \scshape {#1}}\\
		\normalsize #2\\
		\normalsize #3 \hspace*{20pt} 
		\normalsize #4 \hspace*{20pt}
		\normalsize #5
		\lineunder
	\end{center}
	\vspace*{-8pt}
}

\newcommand{\education}[3]{
	{#1} \textbf{#2}\\
	{\hspace*{12pt}#3 }\\ 
	\vspace*{5pt}
}

\newenvironment{resumeContent}{
	\begin{list}
		{\small$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
	\end{list}
}

\newcommand{\resumeheader}[1]{
	\vspace*{5pt}
	\header{\textbf{#1}}
}

\begin{document}
	\normalsize
	\smallskip
	\vspace*{-44pt}

	\contact
		{\bfseries BARRETT D. OTTE}
		{White Hall, Maryland}
		{barrettotte@gmail.com}
		{xxx-xxx-xxxx}
		{barrettotte.github.io}
	
	\resumeheader{SKILLS}
		\textbf{\underline{Main:}} 
			C\#, Java, ColdFusion, Python, C/C++, JavaScript, HTML/CSS, TypeScript, Node.js, Angular, SQL \\ \vspace*{4pt}
		\textbf{\underline{Exposure:}} 
			Groovy, Haskell, Shell, Ruby on Rails, PHP, Assembly x86, BASIC, FORTRAN, RPGLE \\ \vspace*{4pt}
		\textbf{\underline{Database:}} 
			MSSQL, MySQL, MongoDB, PostgreSQL, Cassandra \\ \vspace*{4pt}
		\textbf{\underline{Tools:}} 
			Git, SVN, Bash, Gradle, Ant, Maven, Docker, GitLab CI/CD, Jenkins CI, JIRA, Vim, LaTeX \\ \vspace*{4pt}
		
	\resumeheader{PROJECTS}
		\project
			{MyMovieList}
			{Movie Tracking Web App; Capstone Group Project.}
			{[Node.js, MySQL, HTML/CSS]}
			\begin{resumeContent}
				\item Located at \href{https://github.com/barrettotte/WebApp-MyMovieList}
					{https://github.com/barrettotte/WebApp-MyMovieList}
				\item CRUD (Create, Read, Update, Delete) functionality and sanitization for MySQL database.
				\item Session Handling/Authentication, Heroku Cloud Deployment, Express, EJS, Promises, Helmet.
			\end{resumeContent}
		\project
			{Terrain Generation Self Study}
			{Using perlin noise to generate terrain.}
			{[C\#, Unity Engine]}
			\begin{resumeContent}
				\item Located at \href{https://github.com/barrettotte/Terrain-Generation-Study}
					{https://github.com/barrettotte/Terrain-Generation-Study}
				\item Terrain chunk and procedural octahedral sphere generation using threading and delegates.
				\item LOD enabled terrain chunk scrolling using circular buffer data structure and queue. 
			\end{resumeContent}
		\project
			{Seaport Simulation Project}
			{Object oriented and concurrent programming semester project.} 
			{[Java]}
			\begin{resumeContent}
				\item Located at \href{https://github.com/barrettotte/Seaport-Project}
					{https://github.com/barrettotte/Seaport-Project}
				\item Parse data using internal structure to create ships, people, and ports. Sorted with HashMaps.
				\item Ships compete for open jobs depending on available resources and simulated using threading.
			\end{resumeContent}
		\project
			{Population Genetics Simulation}
			{Simulate mocked DNA in organisms across n generations.}
			{[Python]}
		\project
			{Assembly(x86) HTTP Server}
			{Use system calls and sockets to serve a web page.}
			{[Assembly, NASM]}
		\project
			{MEAN To Do List}
			{Simple to do list using the MEAN Stack.}
			{[MongoDB, ExpressJS, Angular6, Node.js]}
		\project
			{Fortran77-Enigma Machine}
			{WWII enigma machine emulator for simple enigma encryption}
			{[FORTRAN]}
		\project
			{8-Bit Breadboard Computer}
			{Architecture Self Study – ALU, registers, memory, program counter, microcode}
			{}
		\begin{center}
			\vspace*{-3pt}40+ repositories and always growing, located at 
			\href{https://github.com/barrettotte}{https://github.com/barrettotte}
		\end{center}

	\resumeheader{EDUCATION}
		\education
			{University of Maryland University College Graduate 2018:} 
			{Computer Science B.S. Cyber Security Minor}
			{Data Structures and Algorithms, Network Security, Software Engineering, Ethical Hacking, Concurrent
			\hspace*{12pt}Programming, Algorithm Analysis/Design, Computer Architecture, Database Admin.}
		\education
			{Towson University 2015-2016:} 
			{Mathematics and Computer Science B.S. Cyber Security Minor}
			{Statistics (calculus-based), Linear Algebra, Graph Theory, Abstract Algebra, and general coursework}
		\education
			{Harford Community College Graduate 2015:}
			{Computer Science A.S.}
			{Vector and Integral Calculus, Networking, Assembly(x86), Discrete Mathematics, C/C++, Java}
		\education
			{North Harford High School Graduate 2014:} 
			{Computer Science/Computer Information Systems Track}
			{Maryland Scholar, Computer Science, Physics, C++ Programming, Marketing, Java Programming}

	\resumeheader{WORK HISTORY}
		\employer{Goodville Mutual Casualty Company}{New Holland, PA}{Software Developer} {June 2018 - Current} {}
			\vspace*{-8pt}
			\begin{resumeContent}
				\item Exposure to ColdFusion, Java, Angular, MSSQL, XSLT, Groovy, Spring Boot, RPGLE, Gradle, Maven, Ant, Jenkins CI, Agile Development, and JIRA.
				\item Maintain/upgrade legacy ColdFusion and Java code to work towards modernization with microservices using Spring Boot, Angular, and Lucee.
				\item Worked with proof of concept team to automate existing Commercial Umbrella line of business.
			\end{resumeContent}

\end{document}